Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-05 paper/snakemajoranas.tex
changes to the paper

\comment{The symmetry class of the system is D.}
The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.

@@

\comment{We discretize the model described in section II and simulate it with Kwant.}
We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation

@@

\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases by more than an order of magnitude.
This happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
The smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases. 
Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref

\comment{The introduction of an SN interface at many angles also increases performance.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

@@

@@

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the delocalized nature sought after.
All of the zigzag type geometries, however, show significantly reduced coherence length.
Two effects can explain this: the increase in the topological gap, but also the before mentioned reduction of the group velocity.

\comment{We also confirm that the specific shape does not matter.}
Also note the similarity between the various shapes, sharp corners or a smoother system, the effect is the same.

@@

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

>>>>

@@

\comment{We discretize the Hamiltonian and simulate it with Kwant.}
We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation

@@

\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size increases by more than an order of magnitude.
This increase happens because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
The smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases. 
Besides this, the velocity of the modes greatly reduces, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref

\comment{The introduction of an NS interface at many angles increases the transparency.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

@@

\comment{The introduction of the zigzag breaks a chiral symmetry, bringing the system from the BDI to the D symmetry class}
The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.

@@

\comment{We find the Majorana lengths by fitting an exponential to the wavefunction.}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
In figure~\ref{fig:wavefunctions} the wavefunctions are displayed, superimposed upon their respective geometry.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the delocalized nature sought after.
All of the zigzag type geometries, however, show significantly reduced coherence length.
Two effects can explain this: the increase in the topological gap, but also the before mentioned reduction of the group velocity.

\comment{We confirm that the specific shape and its details do not matter.}
Also note the similarity between the various shapes, sharp corners or a smoother system, the effect is the same.

@@

\comment{It is interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like, and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majoranas would be an interesting continuation.
